CF Registry Analysis

### 2023-12-01 Christine Chan/CF Registry/cf_registry_analysis.qmd
output turned out to be a little tricky in parallel

```{r}
# Analysis function
log_reg <- function(year, missingness = T) {
  # Clean data
  df <- annual %>%
    filter(ReviewYear == year, Age_YrEnd >= 10) %>%
    select(
      eDWID, age_group, Gender, bmi_perc, MutClass, A_IsOnEnzymes,
      A_FEV1_pct_predicted, tube_feeding, NumPulmExacerbation,
      A_pseudomonasaeruginosa, A_fungalyeast1, A_mycocultureresults3,
      A_pulmonarycomplications1,
      A_corticosteroids1, cfrd_status_annual, A_Vx770, A_VX809comb,
      liver_disease
    )
  # Assume that missing are CFRD- for these models
  df$cfrd_status_annual[is.na(df$cfrd_status_annual)] <- "CFRD-"
  # Relevel age group since we're excluding kids < 10
  df$age_group <- droplevels(df$age_group)
  # Remove all empty columns
  empty <- which(colSums(is.na(df)) == nrow(df))
  if (length(empty) > 0) {
    df <- df[, -empty]
  }
  # Models
  vars <- colnames(df)[which(!colnames(df) %in%
    c(bugs, liver_fields, "cfrd_status_annual", "eDWID"))]
  base_mod <- as.formula(paste0(
    "cfrd_status_annual~",
    paste0(vars, collapse = "+")
  ))
  # Labels
  labels <- list(
    cfrd_status_annual = "CFRD Status", MutClass = "Mutation class",
    Gender = "Sex", A_IsOnEnzymes = "Pancreatic enzyme use",
    A_FEV1_pct_predicted = "FEV1 percent predicted",
    tube_feeding = "Enteric feedings", liver_disease = "Liver disease",
    A_corticosteroids1 = "Use of corticosteroids",
    NumPulmExacerbation = "Admissions for PEx", age_group = "Age group",
    height_perc = "Height percentile", bmi_perc = "BMI percentile",
    A_Vx770 = "Use of CFTR modulator Vx770",
    A_VX809comb = "Use of CFTR modulator Vx809 combination",
    A_pseudomonasaeruginosa = "Pseudomonas aeruginosa",
    A_fungalyeast1 = "Aspergillus (any species)",
    A_pulmonarycomplications1 = "ABPA",
    A_mycocultureresults3 = "Microorganisms in myco culture"
  )
  var_label(df[, vars[which(vars %in% colnames(df))]]) <-
    as.character(labels[vars[which(vars %in% colnames(df))]])
  var_label(df[, bugs[which(bugs %in% colnames(df))]]) <-
    as.character(labels[bugs[which(bugs %in% colnames(df))]])
  # Visualize missingness if required
  if (missingness) {
    cat("\n")
    cat("### Missingness")
    cat("\n")
    cat("\n")
    print(naniar::vis_miss(df))
    cat("\n")
  }
  # Simple models
  mod1 <- glm(base_mod, data = df, family = "binomial")
  # Print results
  cat("\n")
  cat("### Base Model")
  cat("\n")
  cat("\n")
  print(forest_model(mod1, exclude_infinite_cis = F))
  cat("\n")
  if ("A_pseudomonasaeruginosa" %in% colnames(df)) {
    mod2 <- glm(update(base_mod, . ~ . + A_pseudomonasaeruginosa),
      data = df,
      family = "binomial"
    )
    cat("\n")
    cat("### P. aeruginosa")
    cat("\n")
    cat("\n")
    print(forest_model(mod2, exclude_infinite_cis = F))
    cat("\n")
  }
  if ("A_fungalyeast1" %in% colnames(df)) {
    mod3 <- glm(update(base_mod, . ~ . + A_fungalyeast1),
      data = df,
      family = "binomial"
    )
    cat("\n")
    cat("### Aspergillus")
    cat("\n")
    cat("\n")
    print(forest_model(mod3, exclude_infinite_cis = F))
    cat("\n")
  }
  if ("A_pulmonarycomplications1" %in% colnames(df)) {
    mod4 <- glm(update(base_mod, . ~ . + A_pulmonarycomplications1),
      data = df,
      family = "binomial"
    )
    cat("\n")
    cat("### ABPA")
    cat("\n")
    cat("\n")
    print(forest_model(mod4, exclude_infinite_cis = F))
    cat("\n")
  }
  if ("A_mycocultureresults3" %in% colnames(df)) {
    mod5 <- glm(update(base_mod, . ~ . + A_mycocultureresults3),
      data = df,
      family = "binomial"
    )
    cat("\n")
    cat("### Mycobacterium")
    cat("\n")
    cat("\n")
    print(forest_model(mod5, exclude_infinite_cis = F))
    cat("\n")
  }
}
```

```{r results='asis',fig.height=10,fig.width=10}
cl = makeCluster(16,type = "FORK")
invisible(parLapply(cl,unique(annual$ReviewYear), function(y) {
  cat("\n")
  cat("### ", y)
  cat("\n")
  log_reg(y)
  cat("\n")
}))
stopCluster(cl)
```

>>>>

```{r}
# Analysis function
log_reg <- function(year, missingness = F) {
  # Clean data
  df <- annual %>%
    filter(ReviewYear == year, Age_YrEnd >= 10) %>%
    select(
      eDWID, age_group, Gender, bmi_perc, MutClass, A_IsOnEnzymes,
      A_FEV1_pct_predicted, tube_feeding, NumPulmExacerbation,
      A_pseudomonasaeruginosa, A_fungalyeast1, A_mycocultureresults3,
      A_pulmonarycomplications1,
      A_corticosteroids1, cfrd_status_annual, A_Vx770, A_VX809comb,
      liver_disease
    )
  # Assume that missing are CFRD- for these models
  df$cfrd_status_annual[is.na(df$cfrd_status_annual)] <- "CFRD-"
  # Relevel age group since we're excluding kids < 10
  df$age_group <- droplevels(df$age_group)
  # Remove all empty columns
  empty <- which(colSums(is.na(df)) == nrow(df))
  if (length(empty) > 0) {
    df <- df[, -empty]
  }
  # Models
  vars <- colnames(df)[which(!colnames(df) %in%
    c(bugs, liver_fields, "cfrd_status_annual", "eDWID"))]
  base_mod <- as.formula(paste0(
    "cfrd_status_annual~",
    paste0(vars, collapse = "+")
  ))
  # Labels
  labels <- list(
    cfrd_status_annual = "CFRD Status", MutClass = "Mutation class",
    Gender = "Sex", A_IsOnEnzymes = "Pancreatic enzyme use",
    A_FEV1_pct_predicted = "FEV1 percent predicted",
    tube_feeding = "Enteric feedings", liver_disease = "Liver disease",
    A_corticosteroids1 = "Use of corticosteroids",
    NumPulmExacerbation = "Admissions for PEx", age_group = "Age group",
    height_perc = "Height percentile", bmi_perc = "BMI percentile",
    A_Vx770 = "Use of CFTR modulator Vx770",
    A_VX809comb = "Use of CFTR modulator Vx809 combination",
    A_pseudomonasaeruginosa = "Pseudomonas aeruginosa",
    A_fungalyeast1 = "Aspergillus (any species)",
    A_pulmonarycomplications1 = "ABPA",
    A_mycocultureresults3 = "Microorganisms in myco culture"
  )
  var_label(df[, vars[which(vars %in% colnames(df))]]) <-
    as.character(labels[vars[which(vars %in% colnames(df))]])
  var_label(df[, bugs[which(bugs %in% colnames(df))]]) <-
    as.character(labels[bugs[which(bugs %in% colnames(df))]])
  # Visualize missingness if required
  if (missingness) {
    cat("\n")
    cat("### Missingness")
    cat("\n")
    cat("\n")
    print(naniar::vis_miss(df))
    cat("\n")
  }
  # Simple models
  mod1 <- glm(base_mod, data = df, family = "binomial")
  # Print results
  cat("\n")
  cat("### Base Model")
  cat("\n")
  cat("\n")
  print(forest_model(mod1, exclude_infinite_cis = F))
  cat("\n")
  if ("A_pseudomonasaeruginosa" %in% colnames(df)) {
    mod2 <- glm(update(base_mod, . ~ . + A_pseudomonasaeruginosa),
      data = df,
      family = "binomial"
    )
    cat("\n")
    cat("### P. aeruginosa")
    cat("\n")
    cat("\n")
    print(forest_model(mod2, exclude_infinite_cis = F))
    cat("\n")
  }
  if ("A_fungalyeast1" %in% colnames(df)) {
    mod3 <- glm(update(base_mod, . ~ . + A_fungalyeast1),
      data = df,
      family = "binomial"
    )
    cat("\n")
    cat("### Aspergillus")
    cat("\n")
    cat("\n")
    print(forest_model(mod3, exclude_infinite_cis = F))
    cat("\n")
  }
  if ("A_pulmonarycomplications1" %in% colnames(df)) {
    mod4 <- glm(update(base_mod, . ~ . + A_pulmonarycomplications1),
      data = df,
      family = "binomial"
    )
    cat("\n")
    cat("### ABPA")
    cat("\n")
    cat("\n")
    print(forest_model(mod4, exclude_infinite_cis = F))
    cat("\n")
  }
  if ("A_mycocultureresults3" %in% colnames(df)) {
    mod5 <- glm(update(base_mod, . ~ . + A_mycocultureresults3),
      data = df,
      family = "binomial"
    )
    cat("\n")
    cat("### Mycobacterium")
    cat("\n")
    cat("\n")
    print(forest_model(mod5, exclude_infinite_cis = F))
    cat("\n")
  }
}
```

```{r results='asis',fig.height=10,fig.width=10}
invisible(lapply(unique(annual$ReviewYear), function(y) {
  cat("\n")
  cat("## ", y)
  cat("\n")
  log_reg(y)
  cat("\n")
}))
```
